---
title: "UE20CS312 - Data Analytics - Worksheet 1b - Part 1 - Exploring data with R"
subtitle:"PES University"
author: "Tellakula Mohan Sai, Dept. of CSE - PES1UG20CS468"
date: "2022-08-23"
output: pdf_document
---

```{r}
library(ggpubr)
library(dplyr)
df <- read.csv('road_accidents_india_2016.csv', row.names=1)
```

## Problem-1
Find the total number of accidents in each state for the year 2016 and display your results. Make sure
to display all rows while printing the dataframe. Print only the necessary columns. (Hint: use the grep
command to help filter out column names).
```{r}
col<-grep("Total.Accidents",names(df))
df["Total.Accidents"]=rowSums(df[col])
col<-append(col,2,after=0)
col<-append(col,27)
print(df[col])
```

## Problem-2

```{r}
col2<-grep("Persons.Killed",names(df))
df["Total Deaths"] = rowSums(df[col2])
```


```{r}
df["mist..foggy..rate"]=df$Mist..Foggy...Total.Accidents/(df$Total.Accidents)
df["fatality rate"]=df["Total Deaths"]/df["Total.Accidents"]
result = cor.test(df$`fatality rate`,df$mist..foggy..rate,method = "pearson")
print(result)
```
There is positive correlation between mist..foggy..rate and fatality rate.
```{r}
ggscatter(df,"fatality rate","mist..foggy..rate",cor.coef=TRUE,cor.coeff.args = list(method="pearson"))
```
## Problem-3
```{r}
df["rank_accidents"]=rank(-df$Total.Accidents,ties.method = "first")
df["rank_fatalities"]=rank(-df$`Total Deaths`,ties.method = "first")
```

```{r}
coeff = cor(df$rank_accidents,df$rank_fatalities,method = "spearman")
cor.test(df$rank_accidents,df$rank_fatalities,method = "spearman")
```

```{r}
t_statistic <- (coeff-0.2)/sqrt((1-coeff^2)/(nrow(df)-2))
print(t_statistic)
```
```{r}

```
## Problem-4
```{r}
library(ltm)
df["hail_accident_occcur"]<-ifelse(df$Hail.Sleet...Total.Accidents>0,1,0)
cor.test(df$Rainy...Total.Accidents,df$hail_accident_occcur)
biserial.cor(df$Rainy...Total.Accidents,df$hail_accident_occcur)
```
There is a positive correlation between hail_accident_occcur and Rainy...Total.Accidents.
And Bi-Serial Coefficient is  -0.1429725
## Problem-5
```{r}
library(psych)
df["duststorm_accident_occcur"]<-ifelse(df$Dust.Storm...Total.Accidents>0,1,0)
conmat<-table(df$hail_accident_occcur,df$duststorm_accident_occcur)
phi(conmat)
```