---
title: "UE20CS312 - Data Analytics - Worksheet 1a - Part 1 - Exploring data with R"
author: "Tellakula Mohan Sai,Dept. of CSE - PES1UG20CS468"
date: "2022-08-17"
output:
  html_document:
    df_print: paged
subtitle: PES University
---
## Problem-1
Get the summary statistics (mean, median, mode, min, max, 1st quartile, 3rd quartile and standard deviation)
for the dataset. Calculate these only for the numerical columns [Audience Country, Authentic Engagement
and Engagement Average]. What can you determine from the summary statistics? How does your Instagram
stats hold up with the top 1000 :P ?
```{r}
library(tidyverse)
data <- read_csv("top_1000_instagrammers.csv")
summary(data)
```

```{r}
col<-c("Audience Country","Authentic Engagement","Engagement Avg.")
summary(data[col])
```
Top 1000 instagrammers have an average following of 26044600.
50% of the instagrammers have a following of 14100000.
50% of the instagrammers have authentic engagement of more than 316050 and engagement
average of more than 463300.
Top 25% of Instagrammers have average engagement of more than 850125.

According to the summary my instagram account will be an outlier in this dataset bcs I have only 100 followers.

## Problem-2
What are the top 3 audience countries that follow most of the top 1000 instagrammers? Hint: Go back to
bar graph created earlier. Use R to calculate the percentage of the top 1000 instagrammers that have the top
1 audience country.
```{r}
library('ggplot2')
data$`Audience Country`=replace_na(data$`Audience Country`," ")
ggplot(data, aes(x=`Audience Country`)) + geom_bar() + coord_flip()
```
The Top three Audience Countries are:
1.United States
2.India
3.Brazil
```{r}
US_instagrammers = data[data$`Audience Country`=="United States",1]
fraction<-(nrow(US_instagrammers)/nrow(data))*100
print(fraction)
```
27.7% of Top 1000 Instagrammers have majority audience based in USA.

##Problem-3
Create a horizontal box plot using the column Authentic.Engagement. What inferences can you make from
this box and whisker plot?
```{r}
library('moments')
ggplot(data,aes(y=`Authentic Engagement`))+geom_boxplot()+coord_flip()
```
Most of the values lie below the mean which is 566199.

```{r}
print(skewness(data$`Authentic Engagement`))
```
Distribution of Authentic Engagement is right skewed with skewness of 6.997299

## Problem-4
Create a histogram where the x-axis contains the Audience Country and y-axis contains the total follower
count for accounts with that Audience Country. Which country is associated with the most amount of
followers? Hint: Recall the concept of groupby() in Pandas. Try using the aggregate() function in R to
achieve the same goal. What is the total for India and what rank does it fall compared to other countries?
```{r}
data_c = aggregate(data$Followers,list(data$`Audience Country`),FUN='max')
ggplot(data_c,aes(`Group.1`,`x`))+geom_bar(stat = 'identity')
```
The country with highest number of Followers is India.

## Conclusion
In a few short sentences, describe your Instagram profile (category, followers, estimated engagement). Compare
your profile to the analysis done of the top 1000 profiles. If you were tasked to becoming an influencer, what
would be the best way for you to increase your followers and user engagement?

To have higher followers and user engagement on instagram posting instagram stories,creating new content regularly,etc are the best ways.
